FTLR proof cases

### 2018-06-27 fully-abstract-comp/ftlr-proof-cases.tex
Prove the jmp/jnz case of the FTLR.

  In order to prove this, we first, we prove that one of the following holds:
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\normal),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

@@

      \item(jnz) $\Phi_S' = \updPcAddr{\Phi_S}$ and $\Phi_T' =
        \updPcAddr{\Phi_T}$

@@

@@

    In this case, we can take $R_R' = R_R$ and use Lemma~\ref{lem:purePart-oplus} to give us that all $\purePart{R_R(r)}$ are equal.
    For $r = r_1, r_2, r_3$, we then get easily by definition that
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
    and for other registers, it follows by Lemma~\ref{lem:downwards-closed}.
  \end{itemize}

@@

  TODO
\end{proof}

>>>>

  In order to prove this, we first, we prove that one of the following holds:
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \nstep[j]{\gc} \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$,$j$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\normal),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

      \item \label{case:ftlr:jnz-z} (jnz zero case) $k = 0$

@@

@@

        $\Phi_S(r_1) = \Phi_T(r_1) = ((\perm_1,\lin_1),\baddr_1,\eaddr_1,\aaddr_1)$,
        $\exec{\Phi_S(r_1)}$, $\withinBounds{\Phi_S(r_1)}$,

@@

    In this case, we can take $R_R' = R_R$ and use Lemma~\ref{lem:purePart-oplus} to give us that all $\purePart{R_R(r)}$ are equal.
    For $r = r_1, r_2, r_3$, we then get easily by definition that
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R_R'(r))
    \]
    and for other registers, it follows by Lemma~\ref{lem:downwards-closed}.

  \item Case \ref{case:ftlr:move-cca-etc:jnz-z}:

    In this case, we can take $R_R' = R_R$ and for all registers, the result follows by Lemma~\ref{lem:downwards-closed}.
  \end{itemize}

@@

  We have that
  \begin{itemize}
  \item $\Phi_S \step[\gc] \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
  \item One of the following holds
    \begin{enumproof}
    \item(jmp,jnz) $\Phi_S' = \Phi_S\updReg{\pcreg,r_1}{\Phi_S(r_1),w_1}$ and
      $\Phi_T' = \Phi_T\updReg{\pcreg,r_1'}{\Phi_T(r_1),w_1'}$ and
      $\Phi_S(r_1) = \Phi_T(r_1) = ((\perm_1,\lin_1),\baddr_1,\eaddr_1,\aaddr_1)$,
      $\exec{\Phi_S(r_1)}$, $\withinBounds{\Phi_S(r_1)}$,
      $w_1 = \linCons{\Phi_S(r_1)}$ and $w_1' = \linCons{\Phi_T(r_1)}$
    \item(xjmp) $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) =
      \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and
      $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and
      $c_1' \neq \retptrc(\_)$ and $c_2' \neq \retptrd(\_)$ and
      $\Phi_S'' = \Phi_S\updReg{r_1,r_2}{\linCons{c_1},\linCons{c_2}}$ and $\Phi_S' = \xjumpResult{c_1}{c_2}{\Phi_S''}$ and
      $\Phi_T'' = \Phi_T\updReg{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}$ and
      $\Phi_T' = \xjumpResult{c_1'}{c_2'}{\Phi_T''}$
    \end{enumproof}
  \end{itemize}

  According to Lemma~\ref{lem:lro-anti-red-gen}, it suffices to show:
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]

  In the first case (jmp,jnz), the fact that $\Phi_S$ is reasonable, with $\Phi_S \step[\gc] \Phi_S'$ and $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$, gives us that $\perm_1 = \perm$, $\lin_1 = \normal$, $b_1 = b$, $e_1 = e$.
  The fact that $\lin_1 =\normal$ implies that $w_1 =\Phi_S(r_1)$ and $w_1' = \Phi_T(r_1)$.

  The induction hypothesis tells us that it suffices to prove the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \untrusted$ and $[b,e] \mathrel{\#} \ta$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma, the fact that $\Phi_S \step[\gc] \Phi_S'$ and $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$ and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$:
    See above.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows by Lemma~\ref{lem:downwards-closed} from the fact that $\npair{[b,e]} \in \xReadCond{W_\pcreg}$.
  \item $\npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)$:

    We have that $\Phi_S'.\reg(r) = \Phi_S.\reg(r)$ for all $r \neq \pcreg$, so the result follows by Lemma~\ref{lem:downwards-closed} from the corresponding assumption of this lemma.

  \item $\memSat[n-1]{\Phi_S'.\mem,\Phi_S'.\stk,\Phi_S'.\ms_\stk,\Phi_T'.\mem}{W_M}$:

    These components of $\Phi_S'$ and $\Phi_T'$ are all unmodified from $\Phi_S$ and $\Phi_T$, so the result follows by Lemma~\ref{lem:downwards-closed} from the corresponding assumption of this lemma.

  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined: by assumption.

  \item Theorem~\ref{thm:ftlr} holds for all $n' < n-1$:
    Follows by the same assumption of this lemma.
  \end{itemize}

  In the second case (xjmp), blabla
  TODO
\end{proof}
